Supplement 2

### 2020-09-08 paper/supplement-2.Rmd
edit supplement 2, including figure.

Included articles were: (a) published in 2019; (b) had an accessible
English abstract; (c) had an accessible full text, in English; and (d)
included quantitative data. Studies containing original data, including
case studies (with time-series data) and n=1 trials, were considered.
The search results were imported into EndNote (version 9.3.2).
Duplicates were removed, and titles and abstracts were screened against
the inclusion criteria. Of the articles identified for full text
screening, 10% were sampled, at random, for survey. Because \~30% of the
papers from the initial random sample were not eligible for inclusion
(e.g., full-texts not in English, conference abstracts, qualitative
studies), an additional 5% random sample was taken\--with the
expectation that 30% of the articles from the additional sample would
also be ineligible\--so to preserve a 10% screen of the total papers
published on football related topics in 2019. Figure \@ref(fig:prisma) summarises the search process.

```{r prisma, fig.cap = "Write the figure caption here"}
  # | Imported                        | 3,863                             |
  # | After duplicates removed        | 1,954                             |
  # | After title and abstract screen | 1,373                             |
  # | Random sample full-text         | 199 (needed for 10% sample)       |
  # | Full-text included              | 137                               |
  # | Full-text excluded              | Full-text papers excluded (n=62)  |
  # |                                 | with reasons:                     |
  # |                                 | Qualitative study (n=)            |
  # |                                 | Not in english (n=)               |
  # |                                 | Unable to access full-text (n=)   |

prisma(found = 3863,
       found_other = 0,
       no_dupes = 1954, 
       screened = 1373, # (1954 - 1373) 
       screen_exclusions = 581, 
       full_text = 199,
       full_text_exclusions = 62, 
       qualitative = 0, 
       quantitative = 0,
       width = 800, 
       height = 800)
```

@@

The search returned a total of 3,863 articles (Figure X). Of the 199
articles screened, 136 were deemed eligible, representing \~10% of total
articles published on football related studies in 2019 (Figure X). The
proportion of articles that included a missing data statement (or
acknowledged missing data in a table/figure) was 5.9% \[95% confidence
interval; X% to X%\] or 8/136. A breakdown of the extracted information
is provided in Table XX.

>>>>

Included articles were: (a) published in 2019; (b) in English; 
(c) had an accessible full-text; and (d) included quantitative data. 
Studies containing original data, including case studies (with time-series data) 
and n=1 trials, were considered.
The search results were imported into EndNote (version 9.3.2).
Duplicates were removed, and titles and abstracts were screened against
the inclusion criteria. Of the articles identified for full-text
screening, 10% were sampled, at random, for survey. Because \~30% of the
papers from the initial random sample were not eligible for inclusion
(e.g., full-texts not in English, conference abstracts, qualitative
studies), an additional 5% random sample was taken. It was expected that 
30% of the additional 5% random sample would also be ineligible. With this loss,
it was expected that 10% of the articles that remained after title and abstract 
screening would undergo survey. 
Figure \@ref(fig:prisma) summarises the search process.

```{r prisma, fig.cap = "Write the figure caption here"}
  # | Imported                            | 3,863                             |
  # | After duplicates removed            | 1,954                             |
  # | After title and abstract screen     | 1,373                             |
  # | Random sample for full-text screen  | 199 (needed for 10% inclusion)    |
  # | Full-text included                  | 137                               |
  # | Full-text excluded                  | Full-text papers excluded (n=62)  |

prisma(found = 3863,
       found_other = F,
       no_dupes = 1954, 
       screened = 1373, # (1954 - 1373) 
       screen_exclusions = 581, 
       full_text = 199,
       full_text_exclusions = 62, 
       qualitative = 137, 
       quantitative = 0,
       width = 800, height = 800,
       labels = list(
full_text_exclusions = "Full text articles excluded (n = 62),
with reasons:
Commentary/letter (n = 4),
Conference abstract (n = 21),
Full-text not available (n = 9),
Infographic (n = 2),
Not in English (n = 17),
Qualitative study (n = 9)
"))

@@

The search returned a total of 3,863 articles (Figure 1). Of the 199
articles screened, 136 were deemed eligible, representing \~10% of total
articles published on football related studies in 2019 (Figure X). The
proportion of articles that included a missing data statement (or
acknowledged missing data in a table/figure) was 5.9% \[95% confidence
interval; X% to X%\] or 8/136. A breakdown of the extracted information
is provided in Table XX.
